---
title: "S1PR1"
author: "Uliano"
date: "27/02/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(scales)

source('gromacs1.R')

twocol<-scales::hue_pal()(2)
fourcols<-scales::hue_pal()(4)
#system('./generate_files.sh')
theme_set(theme_gray(base_size = 18))

span<-0.1 # decide quanto sono smoothed le linee dei grafici (+ grande = + smooth)

directories=c('S1PR1_Lys+S1P', 'S1PR1_Lys+FP')
hbonds_tm <- 'hbonds_tm'
saltbr <- 'saltbr'
hbonds_lig <-'hbonds_lig'
dt <- 100
delta <- -0.05
base <- 0.15
diam <- 1
category_name <- 'Ligand'
categories <- c('S1P','FP')
col_names <-c('time','distance')
```

# Global simulation properties

```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'temperature.xvg',category_name,categories,col_names=c('time','value'))
p <- ggplot(df, aes(x=time, y=value, color=Ligand)) + 
  geom_point(alpha=0.3) + 
  geom_smooth(method="loess",span=span,se=FALSE) + 
  labs(title='Temperature', x='Time (ps)',y='(K)') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'min_periodic_distance.xvg',category_name,categories,col_names= c('time','min','max','box1','box2','box3'))
p <- ggplot(df, aes(x=time, y=min, color=Ligand)) + 
  geom_point(alpha=0.3) + 
  geom_smooth(method="loess",span=span,se=FALSE) + 
  labs(title='Minimum distance to periodic image', x='Time (ps)',y='(nm)') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)
```



```{r echo=FALSE, fig.width=10, fig.height=3.5}
time<-c(df$time, df$time)
width<-c(df$box1,df$box3)
side<-gl(2,k=nrow(df),labels=c('xy','z'))
Ligand<-factor(c(as.character(df$Ligand), as.character(df$Ligand)),levels=(c('FP','S1P')))
box<-data.frame(time,width,side,Ligand)
p <- ggplot(box, aes(x=time, y=width, shape=side, color=Ligand)) + geom_point(alpha=0.2)+geom_smooth(method="loess",span=span,se=FALSE) + labs(title='Box size', x='Time (ps)',y='(nm)') +
  guides(colour = guide_legend(override.aes = list(alpha=1)), shape = guide_legend(override.aes = list(alpha=1)))
print(p)
```


```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'rmsd.xvg',category_name,categories,col_names=c('time','value'))
p <- ggplot(df, aes(x=time, y=value, color=Ligand)) + 
  geom_point(alpha=0.3) + 
  geom_smooth(method="loess",span=span,se=FALSE) + 
  labs(title='RMSD', x='Time (ps)',y='(nm)') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)

```


```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'sasa.xvg',category_name,categories,col_names=c('time','value'))
p <- ggplot(df, aes(x=time, y=value, color=Ligand)) + 
  geom_point(alpha=0.3) + 
  geom_smooth(method="loess",span=span,se=FALSE) + 
  labs(title='SASA', x='Time (ps)',y=expression((nm^{2}))) +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)

```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'gyrate.xvg',category_name,categories,col_names=c('time','radius','rx','ry','rz'))
p <- ggplot(df, aes(x=time, y=radius, color=Ligand)) + 
  geom_point(alpha=0.3) + 
  geom_smooth(method="loess",span=span,se=FALSE) + 
  labs(title='Gyration Radius', x='Time (ps)',y='(nm)') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)

```

```{r echo=FALSE, fig.width=10, fig.height=5}
s.rmsf<-read_xvg('S1PR1_Lys+S1P/rmsf.xvg', column_names = c('res','rmsf'))
s.rmsf$seq<-seq(1,nrow(s.rmsf))
s.rmsf$Ligand<-ifelse(s.rmsf$res>1000,'S1P-Lys','S1P')
s.rmsf$grp<-1
f.rmsf<-read_xvg('S1PR1_Lys+FP/rmsf.xvg', column_names = c('res','rmsf'))
f.rmsf$seq<-seq(1,nrow(f.rmsf))
f.rmsf$grp<-2
f.rmsf$Ligand<-ifelse(f.rmsf$res>1000,'FP-Lys','FP')
rmsf<-rbind(s.rmsf,f.rmsf)
p<-ggplot(rmsf, aes(x=seq,y=rmsf,colour=Ligand,group=grp))+geom_line(size=.8)+labs(title='RMSF', x='Residue',y='(nm)')
print(p)

```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'hbnum.xvg',category_name,categories,col_names=c('time','value','v2'))
p <- ggplot(df, aes(x=time, y=value, color=Ligand)) + 
  geom_point(alpha=0.3) + 
  geom_smooth(method="loess",span=span,se=FALSE) + 
  labs(title='Number of H Bonds in Transmembrane part', x='Time (ps)',y='') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)

```


```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'hbnum_lig.xvg',category_name,categories,col_names=c('time','value','v2'))
p <- ggplot(df, aes(x=time, y=value, color=Ligand)) + 
  geom_point(alpha=0.3) + 
  geom_smooth(method="loess",span=span,se=FALSE) + 
  labs(title='Number of H Bonds between Transmembrane and Ligand', x='Time (ps)',y='') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)

```


```{r echo=FALSE, fig.width=10, fig.height=3.5}
```

# Detail of Contacts 

H Bonds were computed with GROMACS using .35 nm for distance cutoff and 30&deg; for angle cutoff.

* meeting of both cutoff conditions is shown in the lower part of the graph. 

* in case more than one H Bond between a pair of residue the minimum distance and the union of angle and distance cutoffs consensus have been considered

Salt Bridges were computed with VMD.

* To be consiedered as a salt bridge a contact should happen such that the minimum distance between any oxygens in the acid residue and any of the niteogens od the basic residue is below a cutoff of 0.32 nm in at least 1 frame. 

* Once the cutoff is reached distance is measured between the center of mass of the oxygens and the center of mass of the nitrogens.

## Potein Protein Contacts

a minimum distance (along the chain) of 4 residues has been considered for both H Bonds and Salt Bridges.



```{r, echo=FALSE}

```

### Helix 1 vs 7

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('ASN63-SER304')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bridges<-c('GLU294-LYS41')
p<-plot_saltbr(directories, saltbr, bridges, category_name, categories, dt=100)
print(p)
```

### Helix 1 vs ICL1

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('HIS77-TRP71')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

## Helix 1 vs C Term

```{r echo=FALSE, fig.width=10, fig.height=5}
bridges<-c('GLU62-ARG319', 'GLU62-ARG328')
p<-plot_saltbr(directories, saltbr, bridges, category_name, categories, dt=100)
print(p)

```

### Helix 2 vs 3

```{r echo=FALSE, fig.width=10, fig.height=13}
bonds<-c('ASN101-ARG120','ASN101-GLU121','ARG120-LEU104','ASN86-SER134','SER131-ASP91')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### Helix 2 vs 4

```{r echo=FALSE, fig.width=10, fig.height=5}
bonds<-c('ASN86-TRP168','TYR82-ASN157')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### Helix 2 vs 6

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('TYR81-GLU250')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### Helix 2 vs 7

```{r echo=FALSE, fig.width=10, fig.height=7}
bonds<-c('ASN307-ASP91','SER304-ASP91','TYR81-ASN315')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### Helix 2 vs ECL1

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('THR108-LEU103')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### Helix 3 vs 4
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('SER129-SER171')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### Helix 3 vs 5
```{r echo=FALSE, fig.width=10, fig.height=5}
bonds<-c('TYR143-ARG223','TYR221-LEU135')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### Helix 3 vs 6
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('ARG142-ASN251')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### Helix 3 vs 7
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('TYR311-ASP91')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### Helix 3 vs N Ter
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('TYR29-TRP117')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```



### Helix 3 vs ICL2
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('MET149-ILE144')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### Helix 3 vs ECL2
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('TYR198-PHE118')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### Helix 3 vs ECL1
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('THR109-ARG120')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### Helix 4 vs 5

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('TYR202-LEU174')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### Helix 4 vs ECL2

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('TRP182-LEU177')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### Network Helix 5 vs Helix 6 vs ECL2

```{r echo=FALSE, fig.width=10, fig.height=13}
bonds<-c('LYS200-ASP279','LYS200-VAL280','LYS200-CYS282','LYS200-SER190','LYS200-CYS191')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bridges<-('ASP279-Lys200')
p<-plot_saltbr(directories, saltbr, bridges, category_name, categories, dt=dt)
print(p)

```


###  Helix 6 vs Helix 7

```{r echo=FALSE, fig.width=10, fig.height=7}
bonds<-c('THR257-THR314','THR257-ASN315','TRP269-ASN303')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


###  Helix 6 vs ICL1

```{r echo=FALSE, fig.width=10, fig.height=5}
bonds<-c('ARG78-GLU250','LYS75-GLU250')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

###  Helix 6 vs ICL1

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('SER192-ASP279')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=5}
bridges<-c('GLU250-ARG78', 'GLU250-LYS75')
p<-plot_saltbr(directories, saltbr, bridges, category_name, categories, dt=100)
print(p)
```

###  Helix 6 vs ECL2

```{r echo=FALSE, fig.width=10, fig.height=5}
bonds<-c('THR193-ASP279','VAL194-ASP279')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```



### Helix 7 N Ter
```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('LYS41-GLU294')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}

```

### N Ter

```{r echo=FALSE, fig.width=10, fig.height=5}
bonds<-c('LEU35-TYR29','LYS34-TYR29')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bridges<-('ASP18-ARG27')
p<-plot_saltbr(directories, saltbr, bridges, category_name, categories, dt=dt)
print(p)
```

### N Ter vs ECL1

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('SER38-TYR110')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
```


### N Ter vs ECL2

```{r echo=FALSE, fig.width=10, fig.height=5}
bonds<-c('LYS34-TYR29','TYR31-LEU188')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


### N Ter vs ECL3

```{r echo=FALSE, fig.width=10, fig.height=5}
bonds<-c('LYS285-TYR31','LYS34-PHE291')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### ICL1 vs C Ter

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('LYS75-GLU317')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bridges<-c('GLU317-LYS75')
p<-plot_saltbr(directories, saltbr, bridges, category_name, categories, dt=100)
print(p)
```

### ECL2

```{r echo=FALSE, fig.width=10, fig.height=5}
bonds<-c('CYS184-LEU197','SER192-TYR198')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### ECL2 vs ECL3

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('THR193-LYS285')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```

### ECL2 vs N Ter

```{r echo=FALSE, fig.width=10, fig.height=3.5}
bonds<-c('HIS28-CYS184')
p<-plot_hbonds(directories, hbonds_tm, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```


## Ligand vs Protein Contacts

### Sphingosine 1 Phosphate H Bonds

|   n.|          Donor          |  Hydrogen   |         Acceptor        | occup.|
|-----|:-----------------------:|:-----------:|:-----------------------:|------:|
|   0 |  TYR 29       OH 238    |   HH 239    |  LIG 1515     O2 7541   |  44%  |
|   1 |  TYR 29       OH 238    |   HH 239    |  LIG 1515     O3 7542   |  19%  |
|   2 |  TYR 29       OH 238    |   HH 239    |  LIG 1515     O4 7543   |  38%  |
|   3 |  LYS 34       NZ 318    |  HZ1 319    |  LIG 1515     O2 7541   |   3%  |
|   4 |  LYS 34       NZ 318    |  HZ1 319    |  LIG 1515     O3 7542   |   2%  |
|   5 |  LYS 34       NZ 318    |  HZ1 319    |  LIG 1515     O4 7543   |   0%  |
|   6 |  SER 38       OG 383    |  HG1 384    |  LIG 1515     O2 7541   |   1%  |
|   7 |  SER 38       OG 383    |  HG1 384    |  LIG 1515     O3 7542   |   2%  |
|   8 |  SER 38       OG 383    |  HG1 384    |  LIG 1515     O4 7543   |   2%  |
|   9 |  ASN 101     ND2 1423   | HD21 1424   |  LIG 1515      N 7544   |  14%  |
|  10 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515      **O 7539**   |   1%  |
|  11 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515     O1 7540   |   5%  |
|  12 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515     O2 7541   |   3%  |
|  13 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515     O3 7542   |   2%  |
|  14 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515     O4 7543   |   5%  |
|  15 |  GLY 106       N 1496   |   HN 1497   |  LIG 1515     O2 7541   |  11%  |
|  16 |  GLY 106       N 1496   |   HN 1497   |  LIG 1515     O3 7542   |  34%  |
|  17 |  GLY 106       N 1496   |   HN 1497   |  LIG 1515     O4 7543   |  33%  |
|  18 |  THR 109     OG1 1533   |  HG1 1534   |  LIG 1515     O2 7541   |  14%  |
|  19 |  THR 109     OG1 1533   |  HG1 1534   |  LIG 1515     O3 7542   |   6%  |
|  20 |  THR 109     OG1 1533   |  HG1 1534   |  LIG 1515     O4 7543   |  16%  |
|  21 |  ARG 120     NH1 1737   | HH11 1738   |  LIG 1515     O2 7541   |   4%  |
|  22 |  ARG 120     NH1 1737   | HH11 1738   |  LIG 1515     O3 7542   |   1%  |
|  23 |  ARG 120     NH1 1737   | HH11 1738   |  LIG 1515     O4 7543   |   4%  |
|  24 |  ARG 120     NH2 1740   | HH21 1741   |  LIG 1515     O1 7540   |   0%  |
|  25 |  ARG 120     NH2 1740   | HH21 1741   |  LIG 1515     O2 7541   |  39%  |
|  26 |  ARG 120     NH2 1740   | HH21 1741   |  LIG 1515     O3 7542   |  15%  |
|  27 |  ARG 120     NH2 1740   | HH21 1741   |  LIG 1515     O4 7543   |  43%  |
|  28 |  LIG 1515      N 7544   |    H 7545   |  ASN 101     OD1 1422   |  31%  |
|  29 |  LIG 1515      N 7544   |    H 7545   |  ARG 120     NH2 1740   |   1%  |
|  30 |  LIG 1515      N 7544   |    H 7545   |  GLU 121     OE1 1756   |  37%  |
|  31 |  LIG 1515      N 7544   |    H 7545   |  GLU 121     OE2 1757   |  37%  |

## Fingolimod H Bonds

|   n.|          Donor          |  Hydrogen   |         Acceptor        | occup.|
|-----|:-----------------------:|:-----------:|:-----------------------:|------:|
|   0 |  TYR 29       OH 238    |   HH 239    |  LIG 1515     O2 7547   |  58%  |
|   1 |  TYR 29       OH 238    |   HH 239    |  LIG 1515     O3 7548   |   4%  |
|   2 |  TYR 29       OH 238    |   HH 239    |  LIG 1515     O4 7549   |  38%  |
|   3 |  LYS 34       NZ 318    |  HZ1 319    |  LIG 1515     O2 7547   |   3%  |
|   4 |  LYS 34       NZ 318    |  HZ1 319    |  LIG 1515     O3 7548   |   0%  |
|   5 |  SER 38       OG 383    |  HG1 384    |  LIG 1515     O2 7547   |   0%  |
|   6 |  SER 38       OG 383    |  HG1 384    |  LIG 1515     O3 7548   |   0%  |
|   7 |  SER 38       OG 383    |  HG1 384    |  LIG 1515     O4 7549   |   1%  |
|   8 |  ASN 101     ND2 1423   | HD21 1424   |  LIG 1515      N 7550   |   2%  |
|   9 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515      **O 7545**   |   7%  |
|  10 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515     O2 7547   |   1%  |
|  11 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515     O3 7548   |   0%  |
|  12 |  SER 105      OG 1492   |  HG1 1493   |  LIG 1515     O4 7549   |   2%  |
|  13 |  GLY 106       N 1496   |   HN 1497   |  LIG 1515     O2 7547   |   3%  |
|  14 |  GLY 106       N 1496   |   HN 1497   |  LIG 1515     O3 7548   |  34%  |
|  15 |  GLY 106       N 1496   |   HN 1497   |  LIG 1515     O4 7549   |  52%  |
|  16 |  THR 109     OG1 1533   |  HG1 1534   |  LIG 1515     O2 7547   |  11%  |
|  17 |  THR 109     OG1 1533   |  HG1 1534   |  LIG 1515     O3 7548   |  13%  |
|  18 |  THR 109     OG1 1533   |  HG1 1534   |  LIG 1515     O4 7549   |  42%  |
|  19 |  ARG 120     NH1 1737   | HH11 1738   |  LIG 1515     O2 7547   |   5%  |
|  20 |  ARG 120     NH1 1737   | HH11 1738   |  LIG 1515     O3 7548   |   0%  |
|  21 |  ARG 120     NH1 1737   | HH11 1738   |  LIG 1515     O4 7549   |   3%  |
|  22 |  ARG 120     NH2 1740   | HH21 1741   |  LIG 1515     O2 7547   |  59%  |
|  23 |  ARG 120     NH2 1740   | HH21 1741   |  LIG 1515     O3 7548   |   3%  |
|  24 |  ARG 120     NH2 1740   | HH21 1741   |  LIG 1515     O4 7549   |  38%  |
|  25 |  ARG 292     NH1 6890   | HH11 6891   |  LIG 1515      **O 7545**   |   2%  |
|  26 |  ARG 292     NH1 6890   | HH11 6891   |  LIG 1515     O1 7546   |   0%  |
|  27 |  ARG 292     NH1 6890   | HH11 6891   |  LIG 1515     O2 7547   |  20%  |
|  28 |  ARG 292     NH1 6890   | HH11 6891   |  LIG 1515     O3 7548   |  19%  |
|  29 |  ARG 292     NH1 6890   | HH11 6891   |  LIG 1515     O4 7549   |   2%  |
|  30 |  ARG 292     NH2 6893   | HH21 6894   |  LIG 1515      **O 7545**   |   3%  |
|  31 |  ARG 292     NH2 6893   | HH21 6894   |  LIG 1515     O1 7546   |   1%  |
|  32 |  ARG 292     NH2 6893   | HH21 6894   |  LIG 1515     O2 7547   |   5%  |
|  33 |  ARG 292     NH2 6893   | HH21 6894   |  LIG 1515     O3 7548   |   3%  |
|  34 |  ARG 292     NH2 6893   | HH21 6894   |  LIG 1515     O4 7549   |   0%  |
|  35 |  LIG 1515      N 7550   |   H1 7564   |  ASN 101     OD1 1422   |  98%  |
|  36 |  LIG 1515      N 7550   |   H1 7564   |  ASN 101       O 1427   |   0%  |
|  37 |  LIG 1515      N 7550   |   H1 7564   |  SER 105      OG 1492   |  77%  |
|  38 |  LIG 1515      N 7550   |   H1 7564   |  ARG 120      NE 1734   |   0%  |
|  39 |  LIG 1515      N 7550   |   H1 7564   |  ARG 120     NH2 1740   |   2%  |
|  40 |  LIG 1515      N 7550   |   H1 7564   |  GLU 121     OE1 1756   |  69%  |
|  41 |  LIG 1515      N 7550   |   H1 7564   |  GLU 121     OE2 1757   |  76%  |

In the above tables ligand hydroxyl oxygens are typeset in **bold**.

```{r echo=FALSE, fig.width=10, fig.height=19}
bonds<-c('TYR29-LIG1515','THR109-LIG1515','SER38-LIG1515','SER105-LIG1515',
         'LYS34-LIG1515','LIG1515-GLU121','GLY106-LIG1515',
         'ASN101-LIG1515','ARG120-LIG1515' )
p<-plot_hbonds(directories, hbonds_lig, bonds, category_name, categories, delta=delta, base=base, diam=diam)
print(p)
```
```{r echo=FALSE, fig.width=10, fig.height=7}
bridges<-c('LIG1515-ARG120','LIG1515-LYS34','GLU121-LIG1515')
p<-plot_saltbr(directories, 'saltbr_lig', bridges, category_name, categories, dt=100)
print(p)
```

# 3x46 switch

```{r 3x46_switch_1, echo=FALSE, fig.width=10, fig.height=5}
file_name <-'mindist_i138_v258.xvg'
df1 <-read_many_files(directories, file_name, category_name, categories, col_names)
df1$interaction<-'3x46 - 6x37'
file_name <-'mindist_i138_y311.xvg'
df2 <-read_many_files(directories, file_name, category_name, categories, col_names)
df2$interaction<-'3x46 - 7x53'
df<-rbind(df1,df2)
p <- ggplot(df, aes(x=time, y=distance, color=Ligand)) +
  geom_point(alpha=0.2) +
  labs(title='Minimum Distance', x='Time (ps)', y='Distance (nm)') +
  geom_smooth(method="loess",span = span,se=F) +
  guides(colour = guide_legend(override.aes = list(alpha=1)))+
  facet_grid(interaction ~ .)+coord_cartesian(ylim=c(0,1))
print(p)
```


```{r 3x46_switch_2, echo=FALSE,fig.width=10, fig.height=5}
file_name <-'ncontact_i138_v258.xvg'
df1 <-read_many_files(directories, file_name, category_name, categories, col_names)
df1$interaction<-'3x46 - 6x37'
file_name <-'ncontact_i138_y311.xvg'
df2 <-read_many_files(directories, file_name, category_name, categories, col_names)
df2$interaction<-'3x46 - 7x53'
df<-rbind(df1,df2)
p <- ggplot(df, aes(x=time, y=distance, color=Ligand)) +
  geom_point(alpha=0.2) +
  labs(title='Number of Contacts < 0.6 nm', x='Time (ps)', y='Number') +
  geom_smooth(method="loess",span = span,se=F) +
  guides(colour = guide_legend(override.aes = list(alpha=1)))+
  facet_grid(interaction ~ .)
print(p)

```
# Clusters


```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'rmsd-distribution.xvg',category_name,categories,col_names=c('rms','au'))
p <- ggplot(df, aes(x=rms, y=au, color=Ligand, group=Ligand)) + 
  geom_line() + 
  labs(title='RMSD Distribution of Transmembrane part', x='RMSD (nm)',y='a.u.') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'rmsd-clust-transitions-0.2.xvg',category_name,categories,col_names=c('clid','ntrans'))
df$clid<-factor(df$clid)
p <- ggplot(df, aes(x=clid, y=ntrans, color=Ligand, fill=Ligand)) + 
  geom_bar(stat="identity", position = "dodge") + 
  labs(title='Cluster transitions', x='Cluster #',y='# transitions') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)

```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'rmsd-clust-id-over-time-0.2.xvg',category_name,categories,col_names=c('time','cluster'))
df$cluster<-factor(df$cluster)
p <- ggplot(df, aes(x=time, y=cluster, color=Ligand, group=Ligand)) + 
  geom_point(alpha=0.2) + 
  labs(title='Clusters', x='Time (ps)',y='Cluster #') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)

```



```{r echo=FALSE, fig.width=10, fig.height=3.5}
df <- read_many_files(directories,'eigenval.xvg',category_name,categories,col_names=c('eig','val'))

df<-subset(df, eig <= 6)

df$eig<-factor(df$eig)
p <- ggplot(df, aes(x=eig, y=val, color=Ligand, group=Ligand)) + 
  geom_point(alpha=1) + 
  labs(title='Eigenvalues', x='Eigenvalue #',y=expression((nm^{2}))) +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)
```



```{r echo=FALSE, fig.width=10, fig.height=13}
df <- read_many_files(directories,'eigrmsf.xvg',category_name,categories,col_names=c('atom','rmsf'))
names(df) <-c("atom", "rmsf", "eig", "Ligand")
p <- ggplot(df, aes(x=atom, y=rmsf, color=Ligand, group=Ligand)) + 
  geom_line() + facet_grid(eig ~ .) +
  labs(title='RMSF per eigenvector of Transmembrane part', x='Atom #',y='RMS (nm)') +
  guides(colour = guide_legend(override.aes = list(alpha=1)))
print(p)
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
```

```{r echo=FALSE, fig.width=10, fig.height=3.5}
```

